%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[backend=bibtex]{biblatex}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{\textbf{#1 --}\hspace{-7pt}}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{jeffreylimbacher.me}{\Large Jeffrey Limbacher}} & Glendale, CA \\
  \href{jeffreylimbacher.me}{jeffreylimbacher.me} & Email: \href{mailto:jeffreylimbacher@gmail.com}{jeffreylimbacher@gmail.com}\\
  Github: \href{https://github.com/JeffreyLimbacher}{github.com/JeffreyLimbacher} & Mobile: (818) 285-9719\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California State University, Northridge}{Northridge, CA}
      {Master of Science in Applied Mathematics;  GPA: 3.94}{Jan. 2016 -- Aug. 2018}
    \resumeSubheading
      {California State University, Northridge}{Northridge, CA}
      {Bachelor of Science in Computer Science and Mathematics;  GPA: 3.97}{Aug. 2010 -- Dec. 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Legalzoom}{Glendale, CA}
      {Statistical Analyst}{Mar. 2018 -- Present}
      \resumeItemListStart
       \resumeItem
          {Used Python and SQL/BigQuery to automate analyses, run statistical tests, and generate visualizations.}
       \resumeItem
          {Developed Bayesian model to forecast subscription revenue for A/B test in Python with uncertainty information.}
       \resumeItem
      	  {Used R to create counter-factuals when A/B testing was not available using time series.}
        \resumeItem
          {Develop Tableau dashboards for monitoring A/B tests and performing automatic statistical tests ($t$-test, $\chi^2$).}
      \resumeItemListEnd

    \resumeSubheading
      {ERC, Inc.}{Edwards Air Force Base}
      {Summer Intern}{Jun. 2017 -- Aug. 2017}
      \resumeItemListStart
        \resumeItem
			{Implemented, benchmarked, and presented findings of a Multigrid Quadtree Poisson solver using MATLAB.}
        \resumeItem
			{Developed a MATLAB visualization dashboard that displayed Hall thruster time series and phase plots.}
		\resumeItem	
			{Wrote and tested parallel C++ \href{https://en.wikipedia.org/wiki/Particle-in-cell}{PIC} octree mesh construction. Used \href{https://en.wikipedia.org/wiki/Z-order_curve\#Coordinate_values}{Morton encoding} to bin particles.}
		\resumeItem
   			{Implemented vectorized \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4592974/}{Cross-Convergent Mapping} using MATLAB to analyze Hall thruster time series data.}
   		\resumeItem
   			{Wrote MATLAB script to deduce \href{https://en.wikipedia.org/wiki/Magic_number_(programming)\#Unnamed_numerical_constants}{magic numbers} for Morton encoding based on dimensions of interleaved vectors.}
      \resumeItemListEnd

    \resumeSubheading
      {California State University, Northridge}{Northridge, CA}
      {Graduate Research Assistant}{Aug. 2016 -- Jan. 2018}
       \resumeItemListStart
        \resumeItem
			{Published paper describing method for calculating the DG-discretized Boltzmann collision integral with the DFT.}
		\resumeItem	
			{Used Intel Fortran with OpenMP/MPI to implement numerical methods. Used C++ for H-matrix approximation.}
		\resumeItem
   			{Gather results from numerical simulations and create visualizations of results using Excel and MATLAB.}
   		\resumeItem
			{Used \href{https://slurm.schedmd.com/}{SLURM}/SSH/GNU tools to batch jobs on HPCs.}
      \resumeItemListEnd


    \resumeSubheading
      {Human Automation Teaming Solutions, Inc.}{Canoga Park, CA}
      {Software Engineer}{Jun. 2014 -- Jun. 2016}
      \resumeItemListStart
        \resumeItem{Worked on a 3-person team that designed and implemented a multi-UAV ground control station in C++/Qt.}
        \resumeItem{Implemented a quaternion-based aircraft simulation (\href{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.50.7824&rep=rep1&type=pdf}{NPSNET}) with \href{https://en.wikipedia.org/wiki/PID_controller}{PID controller} and autopilot.}
		\resumeItem{Used Python to scrape STANAG 4586 data structure definitions from PDF format and output C++ class files.}
		\resumeItem{Implemented Q-Learning in C++ to help a simulated commercial aircraft avoid airspace collisions.}
		\resumeItem{Maintained requirements document, software design diagrams, and user guide for the software.}
		\resumeItem{Programmed network socket to interface with third-party software in a distributed simulation environment.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PUBLICATIONS/TALKS-----------------
\section{Publications/Talks}
\hangindent=.7cm\small{
Alexander Alekseenko, \textbf{Jeffrey Limbacher}. \textit{Evaluating High Order Discontinuous Galerkin Discretization of the Boltzmann Collision Integral in $O(N^2)$ Operations Using the Discrete Fourier Transform}. In: \textit{ArXiv e-prints} (Jan. 2018). \href{https://arxiv.org/abs/1801.05892}{arXiv:1801.05892 \texttt{[math.NA]}}. Presented at the 13th World Congress in Computational Mechanics., New York City, New York.}
\vspace{-2pt}
%-----------PROJECTS-----------------
\section{Awards}
  \resumeSubHeadingListStart
  	\resumeSubItem{Leslie and Terry Cutler Scholarship}{Awarded to students showing promise within their field.}
  	\resumeSubItem{Best Reproducible Research}{Awarded for work in the CSUN Datajam.}
    \resumeSubItem{Outstanding Graduating Senior}{Awarded by the Mathematics Department.}
    \resumeSubItem{Dean's List}
      {Awarded every semester when meeting minimum unit requirements.}  
  \resumeSubHeadingListEnd
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming}{Python (pandas, pymc3), R (ggplot, tidyverse), SQL, C++ (Qt), Fortran (OpenMP, MPI), MATLAB, C\# (ASP.NET), Linux, Git, JIRA}
    \resumeSubItem{Courses}{Software Engineering, Computer Network Software, Data Structures, Algorithms, Numerical Linear Algebra, Numerical PDEs, Statistics, Computational Statistics}
  \resumeSubHeadingListEnd
%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
